Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
paper: ripulito figure
paper: adjusted figures

\documentclass{article}
\usepackage{ijcai16}
\usepackage{times}
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{hyperref}

@@

\begin{figure*}[h!]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3 loss} & {\sc synthetic 3 time} & {\sc synthetic 4 loss} & {\sc synthetic 4 time}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Sparse Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Sparse Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:comparison} Comparison between {\sc SetMargin}
      (orange), {\sc riVOI} (blue), {\sc QI} (green) and {\sc EUS}
      (gray) on the $r=3$ (left) and $r=4$ (right) datasets. Each row
      represents a different sampling distribution for user utility.
      The number of iterations is plotted against the utility loss
      (first and third columns) and the cumulative time (second and
      fourth columns). Thick lines indicate median values over users,
      while standard deviations are shown as shaded areas.}
\end{figure*}

@@

\begin{figure*}[h!]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{2}{c}{{\sc synthetic 4}} &
        \multicolumn{2}{c}{{\sc synthetic 5}}
        \\
        {\sc loss per iter.} & {\sc loss per query} & {\sc loss per iter.} & {\sc loss per query}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_uniform_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_uniform_per_query_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc sparse normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_normal_sparse_per_query_loss}
        \\
        \hline
     \end{tabular}
    }
    \caption{\label{fig:selfcomparison} Comparison for {\sc SetMargin}
      with $k=2,3,4$, in orange, blue and green respectively for the
      $r=4$ (left) and $r=5$ (right) datasets using uniform (top row) and sparse normal (bottom row) distributions. Median and standard deviation utility loss values are reported for increasing number of iterations ($1^{st}$ and $3^{rd}$ columns) and pairwise queries ($2^{nd}$ and $4^{th}$ columns).}
\end{figure*}

@@

\begin{figure*}
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
%        \hline
%        \multicolumn{2}{c}{{\sc loss/time per iter.}} &
%        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
%        \multicolumn{4}{c}{{\sc sparse uniform}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}

>>>>

\documentclass{article}
\usepackage{ijcai16}
\usepackage{times}
%\usepackage{latexsym}
%\usepackage{graphicx}
\usepackage{graphbox}
\usepackage{hyperref}
\usepackage{multirow}

@@

% \begin{figure*}[h!]
%     \centering
%     {\footnotesize
%     \begin{tabular}{cccc}
%         % \hline
%         % {\sc synthetic 3 loss} & {\sc synthetic 3 time} & {\sc synthetic 4 loss} & {\sc synthetic 4 time}
%         % \\
%         % \hline \hline
%         \multicolumn{4}{c}{{\sc Uniform}}
%         \\
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_time} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_time}
%         \\
%         \hline
%         \multicolumn{4}{c}{{\sc Normal}}
%         \\
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_time} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_time}
%         \\
%         \hline
%         \multicolumn{4}{c}{{\sc Sparse Uniform}}
%         \\
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_time} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_time}
%         \\
%         \hline
%         \multicolumn{4}{c}{{\sc Sparse Normal}}
%         \\
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_time} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_loss} &
%         \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_time}
%         \\
%         \hline
%     \end{tabular}
%     }
%     \caption{\label{fig:comparison} Comparison between {\sc SetMargin}
%       (orange), {\sc riVOI} (blue), {\sc QI} (green) and {\sc EUS}
%       (gray) on the $r=3$ (left) and $r=4$ (right) datasets. Each row
%       represents a different sampling distribution for user utility.
%       The number of iterations is plotted against the utility loss
%       (first and third columns) and the cumulative time (second and
%       fourth columns). Thick lines indicate median values over users,
%       while standard deviations are shown as shaded areas.}
% \end{figure*}

\begin{figure*}[h!]
    \centering
    {\footnotesize
    \begin{tabular}{ccccc}
        % \hline
        % {\sc synthetic 3 loss} & {\sc synthetic 3 time} & {\sc synthetic 4 loss} & {\sc synthetic 4 time}
        % \\
        % \hline \hline
        % \multicolumn{4}{c}{{\sc Uniform}}
        \\
        {\sc Uniform}  &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_time} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_time}
        \\
        \hline
         % \multicolumn{4}{c}{{\sc Normal}}
        \\
         {\sc Normal} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_normal_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_normal_per_iter_time} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_normal_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_normal_per_iter_time}
        \\
        \hline
        % \multicolumn{4}{c}{{\sc Sparse Uniform}}
        \\
        {\sc Sparse Uniform} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_time} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_time}
        \\
        \hline
        % \multicolumn{4}{c}{{\sc Sparse Normal}}
        \\
        {\sc Sparse Normal} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_time} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:comparison} Comparison between {\sc SetMargin}
      (orange), {\sc riVOI} (blue), {\sc QI} (green) and {\sc EUS}
      (gray) on the $r=3$ (left) and $r=4$ (right) datasets. Each row
      represents a different sampling distribution for user utility.
      The number of iterations is plotted against the utility loss
      (first and third columns) and the cumulative time (second and
      fourth columns). Thick lines indicate median values over users,
      while standard deviations are shown as shaded areas.}
\end{figure*}

@@

\begin{figure*}[h!]
    \centering
    {\footnotesize
    \begin{tabular}{ccccc}
        % \hline
        % \multicolumn{2}{c}{{\sc synthetic 4}} &
        % \multicolumn{2}{c}{{\sc synthetic 5}}
        % \\
        % {\sc loss per iter.} & {\sc loss per query} & {\sc loss per iter.} & {\sc loss per query}
        % \\
        % \hline \hline
        {\sc uniform} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_4_uniform_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_4_uniform_per_query_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_5_uniform_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_5_uniform_per_query_loss}
        \\
        \hline
        {\sc sparse normal} &        
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_4_normal_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_4_normal_sparse_per_query_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_5_normal_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/synthetic_vs_self_5_normal_sparse_per_query_loss}
        \\
        \hline
     \end{tabular}
    }
    \caption{\label{fig:selfcomparison} Comparison for {\sc SetMargin}
      with $k=2,3,4$, in orange, blue and green respectively for the
      $r=4$ (left) and $r=5$ (right) datasets using uniform (top row) and sparse normal (bottom row) distributions. Median and standard deviation utility loss values are reported for increasing number of iterations ($1^{st}$ and $3^{rd}$ columns) and pairwise queries ($2^{nd}$ and $4^{th}$ columns).}
\end{figure*}

@@

\begin{figure*}
    \centering
    {\footnotesize
    \begin{tabular}{lcccc}
%        \hline
%        \multicolumn{2}{c}{{\sc loss/time per iter.}} &
%        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
%        \multicolumn{4}{c}{{\sc sparse uniform}}
        {\sc uniform} &
        \includegraphics[align=c,width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[align=c,width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[align=c,width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[align=c,width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}
